Meaning of simple rules in investment strategies of algorithmic trading

### 2013-06-05 Article/Article20130603/tewi-paper-template.tex
for each one
del space

\indent For centuries predicting future events was a great challenge for many fields of science \cite{ball07, wu12}. Probably next to the meteorology, most important is the prediction of changes in the financial markets \cite{krutsinger99, satchwell05, schwager02}. It's a big still unresolved task that intrigues and motivates the continuing search \cite{fama91, fama98}. Modern computing capabilities allow to change researcher relationship to predictive challenge. If the purpose of this research is to be effective investment, not the successful prediction, research target should be changed. Many scientific papers were devoted to the problem of investment efficiency, also including the best quality papers, as well as work of at least several Nobel Prize winners. Among the many highly sophisticated research methods \cite{fujimoto03, kompa08, pawlak02, pedrycz97, rua09, raghuraj09, wilinski09} , for years was examined the ability of simple patterns classification in the time series \cite{brock92, cai05, gencay99, lebaron99, satchwell05}. Trying to take advantage of this simple patterns (classification rules) in investment strategies.\\

@@

\section{The test results}
\indent The charts below show the curves of capital accumulation for each quarter of quadrant. Each graph represents one decision-making situation with the best parameter, number of last closures to calculate moving average. Fifth diagram shows the (S1s) cumulative strategy value. Which is the sum of profit of all open positions at this moment. Obviously all component strategies are calculated for the best parameter for each of them.\\
\indent Following tables present the results of conducted simulations aimed at finding the best number of bars required to calculate means (bestMALength). Column "strategy" specifies which strategy was used, "profit" - the cumulative sum of the profit. Third column, "bestCalmar", represents Calmar Ratio which describes profit-to-maximum drawdown ratio. Low Calmar Ratio indicates poor investment performance on a risk-adjusted basis during certain time span. Last column "la" presents the number of open positions.
The study of strategy was carried out on the following markets:
\begin{itemize}
\item currency pairs: EURJPY, USDJPY, GBPUSD, EURUSD,
\item indices: FUS500, BOSSAPLN,
\item commodities: FGOLD. FSILVER.
\end{itemize}
BOSSAPLN is currency index that represents ratio of PLN to four other currencies. Every currency pair used to calculate index has other weight USDPLN (40\%), EURPLN (50\%), GBPPLN (5\%), CHFPLN (5\%).
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for EURJPY} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 26.18 & 5.59 & 24 & 2764\\ \hline 
S1b & -14.77 & -0.67 & 6 & 2660\\ \hline 
S1c & 15.74 & 2.49 & 6 & 2332\\ \hline 
S1d & -4.57 & -0.47 & 21 & 2226\\ \hline 
S1s & 22.54 & 3.25 & Group of MA & 4975\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier

>>>>

\indent For centuries predicting future events was a great challenge for many fields of science \cite{ball07, wu12}. Probably next to the meteorology, most important is the prediction of changes in the financial markets \cite{krutsinger99, satchwell05, schwager02}. It's a big still unresolved task that intrigues and motivates the continuing search \cite{fama91, fama98}. Modern computing capabilities allow to change researcher relationship to predictive challenge. If the purpose of this research is to be effective investment, not the successful prediction, research target should be changed. Many scientific papers were devoted to the problem of investment efficiency, also including the best quality papers, as well as work of at least several Nobel Prize winners. Among the many highly sophisticated research methods \cite{fujimoto03, kompa08, pawlak02, pedrycz97, rua09, raghuraj09, wilinski09}, for years was examined the ability of simple patterns classification in the time series \cite{brock92, cai05, gencay99, lebaron99, satchwell05}. Trying to take advantage of this simple patterns (classification rules) in investment strategies.\\

@@

\section{The test results}
\indent The charts below show the curves of capital accumulation for each quarter of quadrant. Each graph represents one decision-making situation with the best parameter, number of last closures to calculate moving average. Fifth diagram shows the (S1s) cumulative strategy value. Which is the sum of profit of all open positions at this moment. Obviously all component strategies are calculated for the best parameter for each one of them.\\
\indent Following tables present the results of conducted simulations aimed at finding the best number of bars required to calculate means (bestMALength). Column "strategy" specifies which strategy was used, "profit" - the cumulative sum of the profit. Third column, "bestCalmar", represents Calmar Ratio which describes profit-to-maximum drawdown ratio. Low Calmar Ratio indicates poor investment performance on a risk-adjusted basis during certain time span. Last column "la" presents the number of open positions.
The study of strategy was carried out on the following markets:
\begin{itemize}
\item currency pairs: EURJPY, USDJPY, GBPUSD, EURUSD,
\item indices: FUS500, BOSSAPLN,
\item commodities: FGOLD. FSILVER.
\end{itemize}
BOSSAPLN is currency index that represents ratio of PLN to four other currencies. Every currency pair used to calculate index has other weight USDPLN (40\%), EURPLN (50\%), GBPPLN (5\%), CHFPLN (5\%).
\newpage
\begin{table}[!t]
\caption{Profits for all strategy quadrants for EURJPY} 
 \begin{center} 
 \begin{tabular}{|l|l|l|l|l|} 
 \hline \textbf{strategy} & \textbf{profit} & \textbf{bestCalmar} & \textbf{bestMALength} & \textbf{la} \\ \hline  
S1a & 26.18 & 5.59 & 24 & 2764\\ \hline 
S1b & -14.77 & -0.67 & 6 & 2660\\ \hline 
S1c & 15.74 & 2.49 & 6 & 2332\\ \hline 
S1d & -4.57 & -0.47 & 21 & 2226\\ \hline 
S1s & 22.54 & 3.25 & Group of MA & 4975\\ 
\hline \end{tabular} 
 \end{center} 
 \end{table}
\FloatBarrier
